### 2024-06-06 Scripts/Scripts-collection.Rmd
Update Scripts-collection.Rmd

@@

df_too_low <- read.csv((r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\microbiome_species-top_prevalent.csv\head-to-head_comparisons-DNA_concentration_too_low.csv)'))
df_too_low$Percentage_Failed <- df_too_low$Percentage_Failed *100
df_too_low$Percentage_successful <- 100 - df_too_low$Percentage_Failed
plot <- ggbarplot(df_too_low, "Method", "Percentage_successful",
                  color = '#1f78b4',fill='#1f78b4',palette = "#1f78b4",
                  label = F,
                  position = position_dodge(0.9)) + 
  scale_x_discrete(labels= c('CMEM','Power Water','AllPrep DNA')) + 
  labs(x=NULL,y='Percentage of samples with detectable\nDNA after extraction (%)') + theme_bw(base_size = 27)
ggpar(plot,legend = 'bottom',x.text.angle = 30)

@@

@@

```{r Fig S1e}
df_profiles_vegan  <-  read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\microbial_profile-feasibility_validation.csv)",header = TRUE)
metadata = read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\metadata-microbial_profile-feasibility_validation.csv)",header = TRUE)

>>>>

```
### Figure S1
### --------------------------------------------------------------------------------------------------------------------------------------------

@@

df_too_low <- read.csv((r'(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\microbiome_species-top_prevalent.csv\head-to-head_comparisons-DNA_concentration_too_low.csv)')) # save in the same file 'head-to-head_comparisons-DNA_concentration.txt'
df_too_low$Percentage_Failed <- df_too_low$Percentage_Failed *100
df_too_low$Percentage_successful <- 100 - df_too_low$Percentage_Failed
plot <- ggbarplot(df_too_low, "Method", "Percentage_successful",
                  color = '#1f78b4',fill='#1f78b4',palette = "#1f78b4",
                  label = F,
                  position = position_dodge(0.9)) + 
  scale_x_discrete(labels= c('CMEM','Power Water','AllPrep DNA')) + 
  labs(x=NULL,y='Percentage of samples with detectable\nDNA after extraction (%)') + theme_bw(base_size = 27)
ggpar(plot,legend = 'bottom',x.text.angle = 30)

@@

df_mappingrate <- read.csv(r'(G:\Bio-Analysis\Python\Vscode\Task01-NEW\Responses-related\files-reformat\MappingRate_ETAs.csv)')
df_mappingrate$microbial <- 100 - df_mappingrate$HumanMappingRate
df_mappingrate$fold_increase <- 100 - df_mappingrate$HumanMappingRate -1

plot_microbial_reads <- ggboxplot(df_mappingrate, x=NULL, y="microbial",
                              color = "#2077b4", palette =c("#2077b4", "#E7B800", "#FC4E07"),
                              add = "jitter",add.params = list(size = 1.5, alpha = 0.5)) +
  stat_boxplot(geom = "errorbar",width=0.05,color='#2077b4')  +
  scale_x_discrete(labels='Samples') +
  labs(x=NULL,y='Proportion of microbial reads (%)') + theme_bw(base_size = 16)+
  theme(axis.text.x = element_text(angle=30,hjust=0.7,vjust=0.8))

@@

```{r Fig S1e}

df_profiles_vegan  <-  read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\microbial_profile-feasibility_validation.csv)",header = TRUE)
metadata = read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Supplementary_figures\metadata-microbial_profile-feasibility_validation.csv)",header = TRUE)
